Analysis for Project

### 2021-11-04 analysis/analysis.Rmd
Add state and metro fixed effects to the models

```{r}
#try a model
model0 <- glm(below_exp_grade~as.factor(year)+current_grade, 
              data=acs, family=binomial)
model1 <- update(model0, .~.+race)
model2 <- update(model1, .~.+foreign_born+foreign_born_mother+foreign_born_father)
model3 <- update(model2, .~.+degree_mother+degree_father)
model4 <- update(model3, .~.+sqrt(family_income/10000)+own_home+parents_married)

@@

```{r}
#run separate models by grade groups
model4a <- update(model4, data=subset(acs, as.numeric(current_grade)<=7))
model4b <- update(model4, data=subset(acs, as.numeric(current_grade)>7 &
                                        as.numeric(current_grade)<10))
model4c <- update(model4, data=subset(acs, as.numeric(current_grade)>=10))

@@

```{r}
resources_race <- acs %>% 
  group_by(race) %>%
  summarize(prop_held_back=mean(below_exp_grade),
            mean_age=mean(age),
            prop_foreign_born=mean(foreign_born),
            mean_fam_inc=mean(family_income),
            prop_own_home=mean(own_home),
            prop_hs_diploma=mean(degree_father>="HS diploma" | 
                                   degree_mother>="HS diploma"),
            prop_ba_degree=mean(degree_father>="BA degree" | 
                                  degree_mother>="BA degree"),
            prop_parents_married=mean(parents_married),
            mean_age_parents=mean((age_birth_mother+age_birth_father)/2),
            prop_parent_foreign_born=mean(foreign_born_father | 
                                            foreign_born_mother)) %>%
  ungroup() %>%
  filter(!str_detect(race,"Multiracial"))

ggplot(resources_race, aes(x=reorder(race, mean_fam_inc, mean), y=mean_fam_inc))+
  geom_col()+
  coord_flip()
```

```{r}
#make a plot showing difference from middle expectation by model
coef_table <- bind_rows(tidy(model1) %>%
                          filter(str_detect(term, "race") & 
                                   str_detect(term, "/") & 
                                   !str_detect(term, "Multiracial")) %>%
                          mutate(model="model1"),
                        tidy(model2) %>%
                          filter(str_detect(term, "race") & 
                                   str_detect(term, "/") & 
                                   !str_detect(term, "Multiracial")) %>%
                          mutate(model="model2"),
                        tidy(model4) %>%
                          filter(str_detect(term, "race") & 
                                   str_detect(term, "/") & 
                                   !str_detect(term, "Multiracial")) %>%
                          mutate(model="model4"))
ggplot(coef_table, aes(x=reorder(term, estimate, min), y=estimate, color=model, group=model))+
  geom_point(position="dodge")+
  coord_flip()
```

>>>>

```{r}
#try a model
model0 <- glm(below_exp_grade~as.factor(year)+current_grade+as.factor(state)+metro, 
              data=acs, family=binomial)
model1 <- update(model0, .~.+race)
model2 <- update(model1, .~.+foreign_born+foreign_born_mother+foreign_born_father)
model3 <- update(model2, .~.+degree_mother+degree_father)
model4 <- update(model3, .~.+sqrt(family_income/10000)+own_home+parents_married)

@@

```{r}
#run separate models by grade groups
model4a <- update(model4, data=subset(acs, as.numeric(current_grade)<=6))
model4b <- update(model4, data=subset(acs, as.numeric(current_grade)>6 &
                                        as.numeric(current_grade)<=9))
model4c <- update(model4, data=subset(acs, as.numeric(current_grade)>=10))

@@
